Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-10 podc16/paper2.tex
dependency-set algorithm specification

\todo{Let's base everything on C-Structs; it will be easier. We can say that two commands commute when $\sigma\bullet c_1\bullet c_2 =  \sigma\bullet c_2\bullet c_1 $ for every cstruct $\sigma$.}

@@

A dependency-set algorithm exposes the input interface $\texttt{announce}_p\left( c \right)$, where $c$ is a command, and the output interface $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, where $p\in P$ is the process executing the call.  
Moreover, a dependency-set computation algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion ${suggest\left( c, d \right)}^p$, every command in $\{c\}\cup d$ must have been announced before.
    \item For any two suggestions ${suggest\left( c_1, d_1 \right)}^p$ and ${suggest\left( c_2, d_2 \right)}^p$,  if $c_1$ and $c_2$ do not commute (i.e., $\left( c_1,c_2 \right) \in R$) then either $c_1\in d_2$ or $c_2 \in d_1$.
\end{enumerate}

\todo{Plain english version below. Which is better?}

A dependency-set computation algorithm allows processes to announce a command $c$ and to learn about a suggested dependency set for a previously announced command.
Moreover, a dependency-set computation algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item If the dependency set $d$ has been suggested for $c$, then every command in $\aset{c}\cup d$ must have been announced before.
    \item If the dependency set $d_1$ has been suggested for the command $c_1$, the dependency set $d_2$ has been suggested for the command $c_2$, and $c_1$ and $c_2$ do not commute, then either $c_1\in d_2$ or $c_2 \in d_1$.
\end{enumerate}

>>>>

%\todo{Let's base everything on C-Structs; it will be easier. We can say that two commands commute when $\sigma\bullet c_1\bullet c_2 =  \sigma\bullet c_2\bullet c_1 $ for every cstruct $\sigma$.}

@@

A dependency-set algorithm exposes the input interface $\texttt{announce}_p\left( c \right)$, where $c$ is a command, and the output interface $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, where $p\in P$ is the process executing the call.  
Moreover, a dependency-set algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before.
    \item For any two suggestions $\texttt{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\texttt{suggest}_q \left( c_2,\mathcal{D}_2\right)$ (with $p$ possibly equal to $q$),  if $c_1$ and $c_2$ do not commute then either $c_1\in d_2$ or $c_2 \in d_1$.
\end{enumerate}

%\todo{Plain english version below. Which is better?}

%A dependency-set computation algorithm allows processes to announce a command $c$ and to learn about a suggested dependency set for a previously announced command.
%Moreover, a dependency-set computation algorithm must ensure that:
%\begin{enumerate}[noitemsep,nolistsep]
  %  \item If the dependency set $d$ has been suggested for $c$, then every command in $\aset{c}\cup d$ must have been announced before.
  %  \item If the dependency set $d_1$ has been suggested for the command $c_1$, the dependency set $d_2$ has been suggested for the command $c_2$, and $c_1$ and $c_2$ do not commute, then either $c_1\in d_2$ or $c_2 \in d_1$.
%\end{enumerate}
